{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }

### 2017-05-26 Meetings/AUGrelated/mondaymorning_290517.tex
add the monday morning tex file for 29 May

\documentclass[10pt, compress]{beamer}
\usetheme[conference=AUG Monday,venue=Remote, date=08/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
\date{08 May 2017}
\author[Topic 21 Scientific Team]{N. Vianello for the Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \begin{center}
N. Vianello, D. Carralero, Z. Wei, J. Madsen, K. McClements,
M. Agostini, M.Spolaore, D. Aguiam, E. Wolfrum, J. Vicente,
L. Florian, E. Seliunin, J. Galdon-Quiroga, C. Ionita, S. Costea ...
  \end{center}
\end{frame}
\begin{frame}{Objective of Week 17 campaign}
  \begin{itemize}[<+-|alert@+>]
    \item Check shoulder formation and filamentary transport behavior
      at different current keeping $q_{95}$ constant in L-Mode
    \item Check shoulder formation and filamentary transport behavior
      at different current keeping $B_{t}$ constant in L-Mode
    \item Find suitable H-Mode scenario at \emph{high power}
      (compatible with probe operation) for shoulder behavior and
      filamentary transport studies in H-Mode
  \end{itemize}    
\end{frame}
\begin{frame}{L-Mode: Current scan at constant $q_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=\textheight]{pdfbox/30269Shape}}
    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/LambdaDivVsTime}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantq95}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item Reference shot with \textbf{EOC} Shape, 0.8MA, B$_{\phi}$ = -2.5 T, 0.5MW NBI heating,
        fueling in order to keep heating approximately constant during
        the current scan
      \item<2-> The fueling has been reduced at lower current for not
        encountering disruption too early
      \item<3-> Up to 3 seconds 0.6 and 0.8 discharge exibits close
        edge and core density as well as neutral pressure from gauges
        under the dome
      \item<4-> During the discharge complete scan of $\Lambda_{div}$
        from well below to well above 1.
      \item<5> In all the cases the profiles evolve and tends to
        become flatter. Preliminary indication suggest this occurs at
        similar $\Lambda_{div}$
    \end{itemize}

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=AUG Monday,venue=Remote, date=29/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
\date{29 May 2017}
\author[Topic 21 Scientific Team]{N. Vianello for the Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \begin{center}
N. Vianello, D. Carralero, Z. Wei, J. Madsen, K. McClements,
M. Agostini, M.Spolaore, D. Aguiam, E. Wolfrum, J. Vicente,
L. Florian, E. Seliunin, J. Galdon-Quiroga, C. Ionita, S. Costea ...
  \end{center}
\end{frame}
\begin{frame}{Objective of Week 21 campaign}
  \begin{itemize}[<+-|alert@+>]
    \item Compare divertor/midplane fueling effect on filamentary
      transport and profiles without cryo-pumps
    \item Compare profiles with the same fueling with/without cryopums
    \item Determine an H-Mode with the cryopumps matching similar
      divertor pressure and SOL profiles
  \end{itemize}    
\end{frame}
\begin{frame}{Compare divertor/midplane fueling}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item Reference shot with \textbf{EOC} Shape, 0.8MA, B$_{\phi}$ = -2.5 T, 0.5MW NBI heating,
        fueling in order to keep heating approximately constant during
        the current scan
      \item<2-> The fueling has been reduced at lower current for not
        encountering disruption too early
      \item<3-> Up to 3 seconds 0.6 and 0.8 discharge exibits close
        edge and core density as well as neutral pressure from gauges
        under the dome
      \item<4-> During the discharge complete scan of $\Lambda_{div}$
        from well below to well above 1.
      \item<5> In all the cases the profiles evolve and tends to
        become flatter. Preliminary indication suggest this occurs at
        similar $\Lambda_{div}$
    \end{itemize}
